Proximal compact spaces are Corson compact

### 2013-12-27 articles/proximity-corson/proximity-corson.tex
cleanup, slight revisions

\newcommand{\proxgame}[1]{Prox_{D,P}(#1)}
\newcommand{\sproxgame}[1]{sProx_{D,P}(#1)}
\newcommand{\congame}[2]{Con_{O,P}(#1,#2)}
\newcommand{\clusgame}[2]{Clus_{O,P}(#1,#2)}

@@

@@

J. Bell defined a topological space $X$ to be {\it proximal} if $X$ has a compatible uniformity with respect to which the first player has a winning strategy in a certain $\omega$-length game.  As noted by P.J. Nyikos, it follows easily from Bell's results that Corson compact spaces are proximal.  We answer a question of Nyikos by showing that a compact space is proximal iff it is Corson compact.

%A common generalization of metric spaces is the idea of a uniform space, determined by a uniformity of entourages on the diagonal of the square. Proximal uniform spaces are those for which the first player has a winning strategy in this $\omega$-length game due to Bell: the first player chooses an entourage of the space, and her opponent chooses a point close to the point chosen in the previous round, with respect to the entourage chosen in the previous round. As proximal spaces are preserved under $\Sigma$-products, Nyikos has observed that every Corson compact space, a compact space embeddable in the $\Sigma$-product of real lines, must then be proximal. He asked if that implication may also be reversed. We answer his question positively, by way of defining a stronger version of the proximal game which is perfect-information equivalent to Bell's original game for uniformly locally compact spaces.
\end{abstract}

@@

A common generalization of metric spaces is the idea of a {\it uniform space}.  A uniform space is a determined by a collection of supersets of the diagonal in the square (called ``entourages")  satisfying certain conditions.  A uniformity induces in a natural way a topology on $X$, called the {\it uniform topology}.  A topological space $X$ is {\it uniformizable} if there is  a uniformity on $X$ which generates its topology.   Any completely regular space is uniformizable.  See the next section for more complete definitions of these concepts and some of their basic properties.

@@

\begin{defn}
  A \textit{uniform space} is a pair $\<X,\mc{D}\>$ where $X$ is a set, and $\mc{D}$ is a uniformity. A {\it uniformity} is a filter on subsets of $X^2$, called \textit{entourages}, such that for each entourage $D\in \mc D$:
  \begin{itemize}
      \item $D$ is reflexive, i.e., the diagonal $\Delta=\{\<x,x\>:x\in X\}\subseteq D$.
      \item Its inverse $D^{-1}=\{\<y,x\>:\<x,y\>\in D\}\in \mc D$.
      \item There exists $\frac{1}{2}D\in\mc D$ such that
        \[
          2\left(\frac{1}{2}D\right)=\frac{1}{2}D\circ \frac{1}{2}D=\left\{\<x,z\>:\exists y\left(\<x,y\>,\<y,z\>\in \frac{1}{2}D\right)\right\}\subseteq D.
        \]
      %(Let $\frac{1}{2^{n+1}}D$ be shorthand for $\frac{1}{2}(\frac{1}{2^{n}}D)$.)
    \end{itemize}
\end{defn}

\begin{defn}
  The \textit{uniform topology} induced by a uniformity declares a set $U$ to be open if for every $x\in U$, there is some $D\in\mc D$ with $x\in D[x]=\{y: \<x,y\>\in D\}\subseteq U$.   A topological space $X$ is said to be \textit{uniformizable} if there is a uniformity $D$ on $X$ which induces its topology.
\end{defn}

@@

\begin{defn}
  A uniform space $(X,\mathcal D)$ is said to be \textit{proximal} if and only if $\pl D\win\proxgame{X}$.  A topological space is \textit{proximal} iff it admits  a compatible uniformity (i.e., one which induces its topology) which is proximal.
\end{defn}

@@

\begin{defn}
  A topological space $X$ is said to be a {\it $W$-space} if and only if for every $x\in X$, $\pl O\win \congame{X}{x}$.
\end{defn}

@@

\begin{defn}
  The \textit{absolutely proximal game}  proceeds identially to $\proxgame{X}$, except that $\pl D$ may only win in the case that $\<p_0,p_1,\dots\>$ converges.
\end{defn}

@@

\begin{defn}
  A uniform space is {\it uniformly locally compact} if there exists an open symmetric entourage $L$ such that $\cl{L[x]}$ is a compact neighborhood of $x$ for all $x\in X$.  A topological space is uniformly locally compact if it admits a compatible uniformly locally compact uniformity.
\end{defn}

@@

\begin{proof}
  Let $L$ be a uniformly locally compact entourage. Let $\sigma$ be a strategy for $\pl D$ witnessing $\pl D\win \proxgame{X}$. Without loss of generality, we may assume such that $\sigma(p\rest n)\subseteq L$ for all partial attacks $p\rest n$ (so $\cl{\sigma(p\rest n)[x]}\subseteq\cl{L[x]}$ is compact), and that $n > m$ implies $\sigma(p\rest n)\subset \frac{1}{4}\sigma(p\rest m)$.

@@

  Finally, note that since $\tau$ yields refinements of $\sigma$, then $p$ attacks the winning strategy $\sigma$ in $\proxgame{X}$, but since the intersection of a descending chain of nonempty compact sets is nonempty, we have

@@

\begin{defn}
  A space is said to be {\it Corson compact} if and only if it is homeomorphic to a compact set within the $\Sigma$-product $\Sigma\mathbb{R}^\kappa$ of $\kappa$-many real lines, that is:
    \[
      \Sigma\mathbb{R}^\kappa
        =
      \{x\in \mathbb{R}^\kappa: |\{\alpha:x(\alpha)\not=0\}|<\omega\}
    \]
\end{defn}

@@

  \begin{itemize}
    \item Let $\emptyset\in T(\emptyset)$.
    \item Choose $m_\emptyset<\omega$, $h_{\emptyset,i}\in H$ for $i<m_\emptyset$, and $h_{\emptyset,i,j}\in H\cap\cl{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]}$ for $i,j<m_\emptyset$ such that
      \[
        \{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]:i<m_\emptyset\}
      \]
    is a cover for $H$ and such that for each $i<m_\emptyset$
      \[
        \{\frac{1}{4}\sigma(\<h_{\emptyset,i}\>)[h_{\emptyset,i,j}]:j<m_\emptyset\}
      \]
    is a cover for $H\cap\cl{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]}$.
    \item Let $\<i\>, \<i,h_{\emptyset,i}\>$, and $\<i,h_{\emptyset,i},j\>$ be in $T(\emptyset)$ for $i,j<m_\emptyset$.
  \end{itemize}
This ends the construction of $T(\emptyset)$.   We remark that the indexings $i\mapsto h_{\emptyset,i}$ and $(i,j)\mapsto h_{\emptyset,i, j}$ need not be one-to-one; repetition of points is allowed.

@@

  \begin{itemize}
    \item Let $T(a)\subseteq T(a\concat\<x\>)$.
    \item Choose $t=s\concat\<i,h_{s,i},j,x\>$ such that $s\concat\<i,h_{s,i},j\>\in\max(T(a))$ and $x\in \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]$.  Then $s\concat\<i,h_{s,i},j\>$ is the only node of $T(a)$ that will be extended in this step.
    \item Note that, assuming $o(s)\concat\<h_{s,i}\>$ is a legal partial attack against $\sigma$, then
      \[
        x
          \in
        \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
          \subseteq
        \frac{1}{4}\sigma(o(s))[h_{s,i,j}]
      \]
    and
      \[
        h_{s,i,j}
          \in
        \cl{\frac{1}{4}\sigma(o(s))[h_{s,i}]}
          \subseteq
        \frac{1}{2}\sigma(o(s))[h_{s,i}]
      \]
    implies
      \[
        x
          \in
        \sigma(o(s))[h_{s,i}]
      \]
    and thus $o(s)\concat\<h_{s,i},x\>=o(t)$ is a legal partial attack against $\sigma$.
    \item Choose $m_t<\omega$, $h_{t,k}\in H\cap \cl{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]}$ for $k<m_t$, and $h_{t,k,l}\in H\cap\cl{\frac{1}{4}\sigma(o(t))[h_{t,k}]}$ for $k,l<m_t$ such that
      \[
        \{\frac{1}{4}\sigma(o(t))[h_{t,k}]:k<m_t\}
      \]
    is a cover for $H\cap \cl{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]}$ and such that for each $k<m_t$
      \[
        \{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}]:l<m_t\}
      \]
    is a cover for $H\cap\cl{\frac{1}{4}\sigma(o(t))[h_{t,k}]}$.
    \item Note that, assuming $o(t)$ is a legal partial attack against $\sigma$, then
      \[
        h_{t,k}
          \in
        \cl{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]}
          \subseteq
        \frac{1}{2}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
      \]
    and
      \[
        x
          \in
        \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
      \]
    implies
      \[
        h_{t,k}
          \in
        \sigma(o(s)\concat\<h_{s,i}\>)[x]
      \]
    and thus $o(t)\concat\<h_{t,k}\>$ is a legal partial attack against $\sigma$.
    \item For each $k,l<m_t$, put $t\concat\<k,h_{t,k},l\>$ and all of its initial segments in $ T(a\concat\<x\>)$.   This completes the construction of  $ T(a\concat\<x\>)$.

@@

    \item Note that assuming
      \[
        \{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}] : s\concat\<i,h_{s,i},j\>\in\max(T(a))\}
      \]
    covers $H$, then since
      \[
        \{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}] : s\concat\<i,h_{s,i},j,x,k,h_{t,k},l\>\in\max(T(a\concat\<x\>))\setminus\max(T(a))\}
      \]
    covers $H\cap \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]$, we have that
      \[
        \{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}] : t\concat\<k,h_{t,k},l\>\in\max(T(a\concat\<x\>))\}
      \]
    covers $H$.
  \end{itemize}

@@

% Commented out... I just realized that my old results concerning \congame did not assume that the point picker must pick in the intersection of all the sets chosen by O! In fact, O has an easy tactic for the game used in this paper on a one-point compactification of any space: just forbid the last point played, and it can never be repeated. So there is some hope to show that $\pl O \markwin \congame{X}{x}$ if and only if $\pl O \markwin \clusgame{X}{x}$.

% \section{Further possibilities}

% Note a similar characterization of \textbf{Eberlein compacts}.

% \begin{thm}
%   A space $X$ is Eberlein compact if and only if $X$ is compact and $\pl O \markwin \congame{X^2}{\Delta}$ (that is, $\pl O$ has a \textbf{Mark\"ov} winning strategy depending on only the round number and must recent move of $\pl P$).
% \end{thm}

% One might suspect a positive result to the following question.

% \begin{ques}
%   Is it true that for any compact uniform space $X$, $\pl D\markwin\proxgame{X}$ if and only if $X$ is Eberlein compact?
% \end{ques}

% A difficulty in approaching this problem arises upon realizing that $\congame{X}{H}$ and $\clusgame{X}{H}$ are not equivalent for $\pl O$ in the case of limited-information strategies, even when considering just compact spaces $X$ with $H$ being a singleton.

% \begin{ex}
% Let $\oneptcomp{\omega_1}=\omega_1\cup\{\infty\}$ be the one-point compactification of discrete $\omega_1$ by declaring complements of finite subsets of $\omega_1$ to be open. (Such spaces are also known as \textbf{Fort spaces}.) Then $\pl O\win\congame{\oneptcomp\omega_1}{\infty}$ and $\pl O\markwin\clusgame{\oneptcomp\omega_1}{\infty}$, but $\pl O\not\markwin\congame{\oneptcomp\omega_1}{\infty}$.
% \end{ex}

% \begin{proof}
%   The perfect information winning strategy for $\pl O$ in $\congame{\oneptcomp\omega_1}{\infty}$ is evident: each round, $\pl O$ chooses the complement of all non-$\infty$ points chosen by $\pl P$. Since any legal attack by $\pl P$ cannot reside in a finite subset of $\omega_1$, any open neighborhood of $\infty$ contains all but finitely many points chosen by $\pl P$.

%   To see that $\pl O\markwin\clusgame{\oneptcomp\omega_1}{\infty}$, let $A_{\alpha,n}$ be a finite set such that $A_{\alpha,n}\subseteq A_{\alpha,n+1}$ and $\bigcup_{n<\omega}A_{\alpha,n}=\alpha+1$ for each $\alpha<\omega_1$. We define the Mark\"ov strategy $\sigma$ for $\pl O$ in $\clusgame{\oneptcomp\omega_1}{\infty}$ by letting $\sigma(\alpha,n)=\oneptcomp{\omega_1}\setminus \bigcup_{m\leq n}A_{\alpha,m}$. Note that for any arbitrary $\{\alpha_0,\dots,\alpha_{k-1}\}\in [\omega_1]^{<\omega}$, there is some round $n$ such that $\{\alpha_0,\dots,\alpha_{k-1}\}\setminus \bigcup_{m\leq n,i<k}A_{\alpha_i,m}=\emptyset$, and thus no legal attack by $P$ can keep its range completely within $\{\alpha_0,\dots,\alpha_{k-1}\}$.

%   Finally, $\pl O\not\markwin\congame{\oneptcomp\omega_1}{\infty}$ was shown by Nyikos in \cite{nclasses}.
% \end{proof}

@@

\bibitem{nproximal}
  P.J. Nyikos,
  \emph{Proximal and semi-proximal spaces}, preprint.
% \bibitem{nclasses}
%   Nyikos, Peter.
%   \emph{Classes of compact sequential spaces}.
%   etc.
\end{thebibliography}

>>>>

\newcommand{\proxgame}[1]{Prox_{D,P}(#1)}
\newcommand{\congame}[2]{Con_{O,P}(#1,#2)}
\newcommand{\clusgame}[2]{Clus_{O,P}(#1,#2)}

@@

\newcommand{\term}{\textit}

@@

J. Bell defined a topological space $X$ to be \term{proximal} if $X$ has a compatible uniformity with respect to which the first player has a winning strategy in a certain $\omega$-length game.  As noted by P.J. Nyikos, it follows easily from Bell's results that Corson compact spaces are proximal.  We answer a question of Nyikos by showing that a compact space is proximal iff it is Corson compact.
\end{abstract}

@@

A common generalization of metric spaces is the idea of a \term{uniform space}.  A uniform space is a determined by a collection of supersets of the diagonal in the square (called ``entourages")  satisfying certain conditions.  A uniformity induces in a natural way a topology on $X$, called the \term{uniform topology}.  A topological space $X$ is \term{uniformizable} if there is  a uniformity on $X$ which generates its topology.   Any completely regular space is uniformizable.  See the next section for more complete definitions of these concepts and some of their basic properties.

@@

\begin{defn}
  A \term{uniform space} is a pair $\<X,\mc{D}\>$ where $X$ is a set, and $\mc{D}$ is a uniformity. A \term{uniformity} is a filter on subsets of $X^2$, called \term{entourages}, such that for each entourage $D\in \mc D$:
  \begin{itemize}
      \item $D$ is reflexive, i.e., the diagonal $\Delta=\{\<x,x\>:x\in X\}\subseteq D$.
      \item Its inverse $D^{-1}=\{\<y,x\>:\<x,y\>\in D\}\in \mc D$.
      \item There exists $\frac{1}{2}D\in\mc D$ such that
        \[
          2\left(\frac{1}{2}D\right)=\frac{1}{2}D\circ \frac{1}{2}D=\left\{\<x,z\>:\exists y\left(\<x,y\>,\<y,z\>\in \frac{1}{2}D\right)\right\}\subseteq D.
        \]
    \end{itemize}
\end{defn}

\begin{defn}
  The \term{uniform topology} induced by a uniformity declares a set $U$ to be open if for every $x\in U$, there is some $D\in\mc D$ with $x\in D[x]=\{y: \<x,y\>\in D\}\subseteq U$.   A topological space $X$ is said to be \term{uniformizable} if there is a uniformity $D$ on $X$ which induces its topology.
\end{defn}

@@

\begin{defn}
  A uniform space $(X,\mathcal D)$ is said to be \term{proximal} if and only if $\pl D\win\proxgame{X}$.  A topological space is \term{proximal} iff it admits  a compatible uniformity (i.e., one which induces its topology) which is proximal.
\end{defn}

@@

\begin{defn}
  A topological space $X$ is said to be a \term{$W$-space} if and only if for every $x\in X$, $\pl O\win \congame{X}{x}$.
\end{defn}

@@

\begin{defn}
  The \term{absolutely proximal game}  proceeds identially to $\proxgame{X}$, except that $\pl D$ may only win in the case that $\<p_0,p_1,\dots\>$ converges.
\end{defn}

@@

\begin{defn}
  A uniform space is \term{uniformly locally compact} if there exists an open symmetric entourage $L$ such that $\cl{L[x]}$ is a compact neighborhood of $x$ for all $x\in X$.  A topological space is uniformly locally compact if it admits a compatible uniformly locally compact uniformity.
\end{defn}

@@

\begin{proof}
  Let $L$ be a uniformly locally compact entourage. Let $\sigma$ be a strategy for $\pl D$ witnessing $\pl D\win \proxgame{X}$. Without loss of generality, we may assume such that $\sigma(p\rest n)\subseteq L$ for all partial attacks $p\rest n$ (so $\cl{\sigma(p\rest n)[x]}\subseteq\cl{L[x]}$ is compact), and that $n > m$ implies $\sigma(p\rest n)\subseteq \frac{1}{4}\sigma(p\rest m)$.

@@

  Finally, note that since $\tau$ yields subsets of $\sigma$, then $p$ attacks the winning strategy $\sigma$ in $\proxgame{X}$, but since the intersection of a descending chain of nonempty compact sets is nonempty, we have

@@

\begin{defn}
  A space is said to be \term{Corson compact} if and only if it is homeomorphic to a compact set within the $\Sigma$-product $\Sigma\mathbb{R}^\kappa$ of $\kappa$-many real lines, that is:
    \[
      \Sigma\mathbb{R}^\kappa
        =
      \{x\in \mathbb{R}^\kappa: |\{\alpha:x(\alpha)\not=0\}|<\omega\}
    \]
\end{defn}

@@

  \begin{itemize}
    \item Let $\emptyset\in T(\emptyset)$.
    \item Choose $m_\emptyset<\omega$, $h_{\emptyset,i}\in H$ for $i<m_\emptyset$, and $h_{\emptyset,i,j}\in H\cap\cl{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]}$ for $i,j<m_\emptyset$ such that
      \[
        \left\{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]:i<m_\emptyset\right\}
      \]
    is a cover for $H$ and such that for each $i<m_\emptyset$
      \[
        \left\{\frac{1}{4}\sigma(\<h_{\emptyset,i}\>)[h_{\emptyset,i,j}]:j<m_\emptyset\right\}
      \]
    is a cover for $H\cap\cl{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]}$.
    \item Let $\<i\>, \<i,h_{\emptyset,i}\>$, and $\<i,h_{\emptyset,i},j\>$ be in $T(\emptyset)$ for $i,j<m_\emptyset$.
  \end{itemize}
This ends the construction of $T(\emptyset)$.   We remark that the indexings $i\mapsto h_{\emptyset,i}$ and $\<i,j\>\mapsto h_{\emptyset,i, j}$ need not be one-to-one; repetition of points is allowed.

@@

  \begin{itemize}
    \item Let $T(a)\subseteq T(a\concat\<x\>)$.
    \item Choose $t=s\concat\<i,h_{s,i},j,x\>$ such that $s\concat\<i,h_{s,i},j\>\in\max(T(a))$ and $x\in \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]$.  Then $s\concat\<i,h_{s,i},j\>$ is the only node of $T(a)$ that will be extended in this step.
    \item Note that, assuming $o(s)\concat\<h_{s,i}\>$ is a legal partial attack against $\sigma$, then
      \[
        x
          \in
        \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
          \subseteq
        \frac{1}{4}\sigma(o(s))[h_{s,i,j}]
      \]
    and
      \[
        h_{s,i,j}
          \in
        \cl{\frac{1}{4}\sigma(o(s))[h_{s,i}]}
          \subseteq
        \frac{1}{2}\sigma(o(s))[h_{s,i}]
      \]
    implies
      \[
        x
          \in
        \sigma(o(s))[h_{s,i}]
      \]
    and thus $o(s)\concat\<h_{s,i},x\>=o(t)$ is a legal partial attack against $\sigma$.
    \item Choose $m_t<\omega$, $h_{t,k}\in H\cap \cl{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]}$ for $k<m_t$, and $h_{t,k,l}\in H\cap\cl{\frac{1}{4}\sigma(o(t))[h_{t,k}]}$ for $k,l<m_t$ such that
      \[
        \left\{\frac{1}{4}\sigma(o(t))[h_{t,k}]:k<m_t\right\}
      \]
    is a cover for $H\cap \cl{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]}$ and such that for each $k<m_t$
      \[
        \left\{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}]:l<m_t\right\}
      \]
    is a cover for $H\cap\cl{\frac{1}{4}\sigma(o(t))[h_{t,k}]}$.
    \item Note that, assuming $o(t)$ is a legal partial attack against $\sigma$, then
      \[
        h_{t,k}
          \in
        \cl{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]}
          \subseteq
        \frac{1}{2}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
      \]
    and
      \[
        x
          \in
        \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
      \]
    implies
      \[
        h_{t,k}
          \in
        \sigma(o(s)\concat\<h_{s,i}\>)[x]
      \]
    and thus $o(t)\concat\<h_{t,k}\>$ is a legal partial attack against $\sigma$.
    \item For each $k,l<m_t$, put $t\concat\<k,h_{t,k},l\>$ and all of its initial segments in $ T(a\concat\<x\>)$.   This completes the construction of  $ T(a\concat\<x\>)$.

@@

    \item Note that assuming
      \[
        \left\{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}] : s\concat\<i,h_{s,i},j\>\in\max(T(a))\right\}
      \]
    covers $H$, then since
      \[
        \left\{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}] : s\concat\<i,h_{s,i},j,x,k,h_{t,k},l\>\in\max(T(a\concat\<x\>))\setminus\max(T(a))\right\}
      \]
    covers $H\cap \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]$, we have that
      \[
        \left\{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}] : t\concat\<k,h_{t,k},l\>\in\max(T(a\concat\<x\>))\right\}
      \]
    covers $H$.
  \end{itemize}

@@

@@

\bibitem{nproximal}
  P.J. Nyikos,
  \emph{Proximal and semi-proximal spaces}, preprint.
\end{thebibliography}
